\LARGE \bf TODO Name this thing

### 2012-02-17 papers/itsc_2012/root.tex
paper: intersection policies

@@

in realtime, safely!

and architecture review (generators and thread pool)

@@

when is an agent waiting?

and future plans

@@

@@

>>>>

illustration of turn conflicts

@@

\commentd{architecture review (generators and thread pool)}

Once an agent's route is ready, the agent waits alongside its starting edge. At
the beginning of each tick, they enter with zero initial speed, if it is safe to
do so. The queue for the edge determines safety. Because behaviors must enforce
speed limit along an edge by the time an agent enters the road, then if there is
no agent within the worst-case distance (travel distance at the speed limit,
plus stopping distance) before the spawn point, then the new agent may enter,
whether the simulation is running or paused. It is unnecessary to predict which
agents could enter the edge soon. As a result, there is a buffer space at the
beginning of the edge where a new agent may never spawn. This disqualifies some
short edges from being spawn points, but this is not an issue.

@@

Agents and behaviors (on behalf of an agent) poll an intersection as they
approach it, asking if they should stop or not. A policy is free to prevent
agents from performing conflicting turns concurrently by any means. Two main
policies exist already, but implementing the interface for extensions is simple.

The stop sign policy works by maintaining a current owner and a queue of waiting
agents. An agent can enter the queue only when they are within some threshold of
the start of their turn (a constraint satisfied by the default lookahead
behavior), even if that is several (rather short) edges and turns away. After
the head of the queue has waited for a configurable pause, they obtain the lock
and have exclusive access to the intersection.

A form of deadlock is possible in a sequence of short edges and turns. Agent
$A_1$ acquires the lock to intersection $V_1$, but needs the lock to $V_2$ to
proceed. Meanwhile, $A_2$ has the lock for $V_2$ and needs the lock for $V_1$.
To deal with this circumstance, an agent's behavior can yield any held locks (a
notion generalized to any intersection policy) when its speed is $0$ and its
conservative acceleration is to remain at rest. The stop sign policy only
removes an agent's lock if it has not started its turn (because otherwise, the
agent is stalling in the intersection). The next time that agent polls, the
policy restores the agent to the front of the queue.
\commentd{hopefully we'll have a neater solution than this soon}

\commentd{describe traffic signal policy, once it's working}

Intersection policies are one of the most intriguing piece of the simulation to
tweak. Future policies will include stop lights that adaptively learn better
timings and an AIM-esque reservation system.

@@

TODO

@@

big future ideas:
  contraflow
  microtolling
  dynamic replanning
    autonomous intersections
